\documentclass[11pt]{beamer}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphics}
\usepackage{multicol}
\usepackage{color}
\usepackage{stmaryrd}\usefonttheme[onlymath]{serif}

\title{Progess Report 4}
\date{\today}
\author{Xie Li}
\begin{document}
\maketitle

\begin{frame}\frametitle{Overview of the Progress}
\begin{itemize}
\item Sample-based Algorithm.
\item Reading a chapter of BDD of handbook.
\item A brief summary of algorithms and techniques.
\item Build the gap between LLVM IR and our own data structure.
\item Configured the use of CMake and LLVM API for developing.
\item Investigate \textsc{Spot}.
\end{itemize}

\end{frame}

\begin{frame}\frametitle{Sample based Algorithm}

\begin{itemize}
\item LLVM IR $\Rightarrow$ CFG $\Rightarrow$ Automaton $\mathcal{A}$

\item LTL/LTLf $\Rightarrow$ Automaton(BA/DFA) $\mathcal{P}$

\item Sample paths of $\mathcal{A}\times \mathcal{P}$ on the fly 

$\Rightarrow$

check feasibility of the path


\end{itemize}

\end{frame}

\begin{frame}\frametitle{Properties}

\begin{itemize}
\item Reachability problem: avoidance of errornous states. Here the ``error'' may be given by statement \texttt{error()} in the source.

LTL: $\textbf{G} ! \texttt{error()}$


\item Overflow problem: can be encoded as 
\[-\texttt{maxInt}\le x \le \texttt{maxInt}\]

\item Free and Deref of pointers: can be represented as LTL formula or reachability problem.


\item Devided by zero.

\item Use after free, use without definition.


\item Termination.

\item No Deadlocks.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Algorithms}
\begin{itemize}
\item  Sampled-based MC: SMT solver for feasibility checking, sampling strategy, on-the-fly product.
\item Symbolic MC: BDD library for the encoding of the formula and conditions, SMT solver for checking.

\item Bounded MC: 

\end{itemize}
\end{frame}


\begin{frame}\frametitle{Current Progress of Coding}
Source code available at
\begin{center}
\texttt{https://github.com/SpencerL-Y/LLVMADT}
\end{center}
\end{frame}

\end{document}